### 2017-10-10 paper.tex
figure legend and image update

>>>>

\textbf{Fig 1. Graphical abstract of ten simple rules for collaborative lesson development.} \textbf{1.} To clarify your audience, consider writing learner profiles (see Box 1). \textbf{2.} Make lessons modular by breaking them into small, single-purpose modules. \textbf{3.} Teach your instructors the best practices for developing, delivering, and maintaining lessons. \textbf{4.} Encourage and empower contributors by making the contribution process transparent and straightforward. \textbf{5} Build a community around lessons by creating opportunities for participation and mentorship. \textbf{6.} Publish new version periodically and recognize contributors by their unique identifiers (e.g., ORCID). \textbf{7.} Evaluate lessons during and after class for a complete picture of the lessons' efficacy. \textbf{8.} Reduce, re-use, or recycle lessons before creating a new one from scratch. \textbf{9.} Link to other resources that complement the lesson content. \textbf{10.} Remember that you can't please everyone in your audience or community.
